\subsection{Music Transcription}
In music, transcription is the process of creating a music sheet from a piece or sound. The sheet contains music notation, which consists of different symbols that can be interpreted by musicians, hence it is important for various reasons. Without it composers such as Mozart and Beethoven couldn't have passed their masterpieces across generations. In modern days it helps musicians play songs they never heard before. It's also universal so even if two musicians don't speak the same language, they can read the same notation.

\subsubsection{Traditional Music Transcription}
In the beginning transcription was done by humans. It's also called musical dictation in ear training pedagogy. \cite{human_transcription} It is a skill by which musicians learn to identify pitches, intervals, melody, chords and other elements of music solely by hearing. It is a really hard skill, requires serious training and study and even the best don't have 100\% accuracy. \par

There are some tools to help with the process:
\begin{itemize}
	\item Musical instruments, help musicians test for certain sounds, trying to mimic what they hear
	\item Tape recorders
	\item Nowadays software
\end{itemize}

\subsubsection{Automated Music Transcription}
The term "Automated Music Transcription" was used for the first time in 1977, by audio researchers James A. Moorer, Martin Piszczalski, and Bernard Galler \cite{transcription}. With their knowledge about digital engineering they believed that computers could be programmed to analyze digital recordings of songs such that they could identify things like rhythm, melodies, pitch, bass lines. It's not an easy task. For more than three decades researchers have been trying to crack it open. \par

Fundamentally, AMT is about identifying the pitch and duration of played notes, so they can be converted in traditional music notation on a sheet. \par

It has many advantages over traditional transcription:
\begin{itemize}
	\item Aids experienced musicians in the process of transcribing pieces, increasing their accuracy.
	\item Makes music transcription available to more people, especially beginners, giving them a chance to share their ideas with others.
	\item Helps people learn new songs. There are a lot of music sheets online that are not free. 
	\item It speeds up the process. Manual transcription takes a lot of time.
\end{itemize}